Covid-19 A Spatio-Temporal Investigation.

### 2021-01-08 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 With the whole world being affected by the pandemic, it's a matter of great importance that studies about the Spatio-temporal aspects of the Covid-19 pandemic should be conducted, by evaluating the number of cases and deaths in different countries accordingly to time in the year 2020, we can contribute with methods to analyze Spatio-temporal behavior in future disease outbreaks.

 The main goal of this paper is to present methods used to identify spatial and spatio-temporal dependence in the number of infections and deaths caused by COVID-19, so they can be used in future or hypothetical situations where is necessary to investigate the behavior of a pathogen agent in space and time. The spatial method was calculated by using the Global Moran's I and the Local Moran's I $\!\!^4$, which is also known as a LISA statistic (Local Indicator of Spatial Association), both being used as indicators of spatial association. Spatio-temporal association was evaluated by computing a spatio-temporal Poisson scan statistic, proposed by Kulldorff $\!\!^5$ to identify emerging or "alive" *clusters* in space and time.

>>>>

 With the whole world being affected by the pandemic, it's a matter of great importance that studies about the spatio-temporal aspects of the Covid-19 pandemic should be conducted, so the main goal of this paper is to present methods used to identify spatial and spatio-temporal dependence in the number of infections and deaths caused by Sars-Cov-2 in different countries accordingly to time in the year 2020, so they can be used in future or hypothetical situations where is necessary to investigate the behavior of a pathogen agent in space and time.

 The spatial method was calculated by using the Global Moran's I and the Local Moran's I $\!\!^4$, which is also known as a LISA statistic (Local Indicator of Spatial Association), both being used as indicators of spatial association. Spatio-temporal association was evaluated by computing a spatio-temporal Poisson scan statistic, proposed by Kulldorff $\!\!^5$ to identify emerging or "alive" *clusters* in space and time.
